
```{r 'check_ps', include=FALSE}

user.name = 'Jane Doe'
```

## Mindestlohn und Firmenprofitabilität: Eine interaktive Analyse

Note: Always save your solution files with UTF-8 Encoding!

Example of an RTutor interactive Problemset

Adapt the working directory below and run the setup chunk in RStudio. This creates the problem set files and the sample solution from this solution file. 

## Einführung in den Mindestlohn


Quiz: Auf welche Höhe schätzen Sie den gesetzlichen Mindestlohn in Großbrittanien zur Einführung 1999 (in Pfund)?

- "3.60" [x]

- "5.70" [ ]

- "7.80" [ ]



Quiz: Wie werden Lohnerhöhungen hauptsächlich gedeckt?

- Verkleinerung der Gewinnmarge [x]

- Weitergabe an Verbraucher [ ]

- Effizienzsteigerung [ ]


## Exercise 2 -- Schaubilder

Es soll überprüft werden, wie sich die Einführung des Mindestlohns auf die unterschiedlichen Einkommen ausgewirkt hat. 
Um die Veränderung des Lohns zum Vorjahr zu messen, muss der Datensatz zunächst für jedes einzelne Jahr aufgeteilt werden.

Zu Beginn wird der Datensatz eingelesen.

```{r "1_1"}
dat_main = read_dta('main_fame.dta')
```
Nun wird für jedes Jahr ein eigener Datensatz erstellt. Dafür muss der Datensatz gefiltert werden.

```{r "1_2"}
#
pcw95 = dat_main %>%
  filter(year == 1995)
```



## Exercise 3 -- Difference in Difference

Bei der Difference in Difference (DiD) Methode werden die Daten anhand von zwei Kriterien unterteilt.
Zum einen wird entschieden, ob es sich um eine Pre-Treatment oder eine Post-Treatment Gruppe handelt.


Quiz: Ab welchem Zeitpunkt werden Daten der Post-Treatment Gruppe zugewiesen?

- 1999 [ ]

- 2000 [x]




## Exercise 1 -- Datenübersicht

a) We often want to compute some summary statistic of a vector. For example:

```{r "3_a"}
x = 10:23
# Computing the sum of x
sum(x)
```

Now compute the mean of x.
```{r "3_a_2",optional=TRUE}
# Note the chunk option optional = TRUE means
# the user can continue with the next exercise
# without having solved this one

mean(x)
```


info("useful functions for numeric vectors")



b) Let `y` be a vector that contains the squared elements of `x`, i.e. for each element $i$ we want $$y_i = x_i^2.$$ Then show `y`.
```{r "3_b"}
# We should not set this chunk optional
# since we need y in the next chunk
y = x^2
y
```

c) Now use the function `qplot` from the package `ggplot2` to create a scatter plot of `x` against `y`. You can google `r qplot` to get the help for the function `qplot`.

```{r "3_c",optional=TRUE, dev='svg', fig.width=4}
library(ggplot2) # load ggplot2 package

# Enter your call to qplot here...
qplot(x,y)
# The block above allows the user to add extra arguments to the call to qplot, i.e. qplot(x,y,xlab="The variable x"), would also pass the test.
```



Quiz: What is the 'oddest' prime?

- 2 [x]

- 3 [ ]

- 5 [ ]

- 7 [ ]


Note: A quiz as specified below only works in the shiny environment. If you want to design a quiz in an RMarkdown based RTutor problem set, you should use a chunk. E.g. as follows:

Which of the following numbers is the oddest prime? 2,3,5 or 7? Enter you solution in the code below and press "check".

```{r "3_c_2"}
2
```

## Exercise Submitting your solution

To submit your solution please proceed as follows:

1. Scroll to the top and click on the icon with the bars <i class="fa fa-tasks fa-fw"></i> to see how many points you got so far. If you want to have more points you can try to solve the missing tasks.

2. If you want to submit click on the download button <i class="fa  fa-download fa-fw"></i> at the very right.

3. In the opened tab click the button "Download Submission File". Your browser should then download a file with the extension `.sub`.

4. Upload that downloaded file to your course management system like Moodle, as specified by your instructor.



