## Mindestlohn und Firmenprofitabilität: Eine interaktive Analyse

Example of an RTutor interactive Problemset

Adapt the working directory below and run the setup chunk in RStudio. This creates the problem set files and the sample solution from this solution file. 
#< ignore
```{r "setup"}
library(RTutor)
# Adapt working directory
setwd("C:/Users/lasse/Documents/GitHub/RTutorMindestlohn/inst/Mindestlohn")
ps.name = "Mindestlohn"; sol.file = paste0(ps.name,"_sol.Rmd")
# character vector of all packages you load in the problem set
libs = c("ggplot2","haven") 
create.ps(sol.file=sol.file, ps.name=ps.name,libs=libs, rps.has.sol=TRUE, addons="quiz")
# Show the problem set in the webbrowser
show.ps(ps.name,sample.solution=FALSE,auto.save.code = TRUE)
```
#>

## Einführung in den Mindestlohn

#< quiz "1"
question: Auf welche Höhe schätzen Sie den gesetzlichen Mindestlohn in Großbrittanien zur Einführung 1999 (in Pfund)?
sc:
    - "3.60"0163*
    - "5.70" 
    - "7.80" 

success: Korrekt. Der Artikel befasst sich mit der Einführung des Mindestlohns in Höhe von 3.60 Pfund.
failure: Diese Schätzung ist zu hoch.
#>

#< quiz "2"
question: Wie werden Lohnerhöhungen hauptsächlich gedeckt?
sc:
    - Verkleinerung der Gewinnmarge*
    - Weitergabe an Verbraucher
    - Effizienzsteigerung

success: Auf diese Vermutung beruht der wissenschaftliche Artikel.
failure: Eine mögliche Antwort
#>

## Exercise 2 -- Schaubilder

Es soll überprüft werden, wie sich die Einführung des Mindestlohns auf die unterschiedlichen Einkommen ausgewirkt hat. 
Um die Veränderung des Lohns zum Vorjahr zu messen, muss der Datensatz zunächst für jedes einzelne Jahr aufgeteilt werden.

Zu Beginn wird der Datensatz eingelesen.

```{r}
#< task
dat_main = read_dta('main_fame.dta')
#>
```
Nun wird für jedes Jahr ein eigener Datensatz erstellt. Dafür muss der Datensatz gefiltert werden.

```{r}
#< fill_in
pcw95 = dat_main %>%
  filter(___ == 1995)
#>
#
pcw95 = dat_main %>%
  filter(year == 1995)
```



## Exercise 3 -- Difference in Differences

Bei der Difference in Difference (DiD) Methode werden die Daten anhand von zwei Kriterien unterteilt.
Zum einen wird entschieden, ob es sich um eine Pre-Treatment oder eine Post-Treatment Gruppe handelt.

#< quiz "3"
question: Ab welchem Zeitpunkt werden Daten der Post-Treatment Gruppe zugewiesen?
sc:
    - 1999
    - 2000*

success: Richtige Antwort. Die Einführung war zwar im Jahr 1999, die Daten jedes Jahres beziehen sich allerdings auf das vergangene Geschäftsjahr (April bis März).
failure: Das ist nicht korrekt. 
#>

Für eine DiD-Schätuung muss weiter eine Kontroll- und eine Treatmentgruppe definiert werden. In der Treatmentgruppe werden jene Unternehmen zusammengefasst, bei denen der Durchschnittslohn (avwage) im Jahr unter 12000 Pfund lag.
Die Kontrollgruppe umfasst Unternehmensdaten mit einem Durchschnittslohn zwischen 12000 und 20000 Pfund.

Mit einem Blick auf den Datensatz erkennt man, dass hierfür bereits Dummy-Variablen ertellt worden sind.
ctreat bezieht sich auf die Kontrollkomponente, während "NMW" angibt, ob sich die Daten der Pre- oder Post-Treatment Periode angehören.

```{r}
#< task
dat_table_DiD = dat_main %>%
  group_by(ctreat1, NMW)%>%
  filter(pp == 1) %>%
  summarise(mean_avwage = mean(avwage), mean_ln_avwage = mean(ln_avwage), mean_net_pcm = mean(net_pcm))
#>
```

Nachdem die relevanten Daten des DiD zusammengefasst in der Tabelle "dat_table_DiD" vorhanden sind, können die Differenzen nun händisch berechnet werden.

Die Formel hierfür lautet 
(y.post.treat - y.post.control) - (y.pre.treat - y.pre.control)

```{r}
#< fill_in
# Weisen Sie den für die DiD Schätzung relevanten Variablen die passenden Tabelleneinträge aus "dat_table_DiD" zu.
y1.post.treat = dat_table_DiD$mean_ln_avwage[___]
y1.post.control = dat_table_DiD$mean_ln_avwage[___]
y1.pre.treat = dat_table_DiD$mean_ln_avwage[___]
y1.pre.control = dat_table_DiD$mean_ln_avwage[___]

#>
```

#< quiz "4"
question: Wieso werden für den Durchschnittslohn logarithmierte Werte verwendet?
sc:
    - a*
    - b
    - c

success: Korrekt. 
failure: Das ist nicht die richtige Lösung.
#>

Neben des logarithmierten Durchschnittslohns wird auch der DiD-Schätzer der Nettorendite eines Unternehmens je Geschäftsjahr (net_pcm) berechnet.
Das geschieht analog zur obigen Schätzung.

```{r}
#< task
y2.post.treat = dat_table_DiD$mean_net_pcm[___]
y2.post.control = dat_table_DiD$mean_net_pcm[___]
y2.pre.treat = dat_table_DiD$mean_net_pcm[___]
y2.pre.control = dat_table_DiD$mean_net_pcm[___]
#>
```

Dadurch erhalten wir folgende 


## Exercise 1 -- Datenübersicht

a) We often want to compute some summary statistic of a vector. For example:

```{r}
#< task
x = 10:23
# Computing the sum of x
sum(x)
#>
```

Now compute the mean of x.
```{r optional=TRUE}
# Note the chunk option optional = TRUE means
# the user can continue with the next exercise
# without having solved this one

mean(x)
#< hint
cat("There already exist R functions for many things. To find them use Google, e.g. search for 'R compute mean'.")
#>
```


#< info "useful functions for numeric vectors"
Here are examples for useful R functions
```{r}
max(c(1,5,2)) # returns maximum
min(c(1,5,2)) # returns minimum

sum(c(1,5,2,NA), na.rm=TRUE) # returns sum of all numbers, ignore NA
cumsum(c(1,5,2)) # returns cummulated sum
diff(c(1,5,2)) # returns the vector of differences
```
#>


#< award "mean means mean"
Well, in some occasions one can just guess the name of an R function. The function to compute the mean of a vector, or matrix is called 'mean'. Usually, it is much quicker to goggle than to guess function names, however.
#>

b) Let `y` be a vector that contains the squared elements of `x`, i.e. for each element $i$ we want $$y_i = x_i^2.$$ Then show `y`.
```{r}
# We should not set this chunk optional
# since we need y in the next chunk
y = x^2
y
```

c) Now use the function `qplot` from the package `ggplot2` to create a scatter plot of `x` against `y`. You can google `r qplot` to get the help for the function `qplot`.

```{r optional=TRUE, dev="svg", fig.width=4}
#< task
library(ggplot2) # load ggplot2 package

# Enter your call to qplot here...
#>
qplot(x,y)
#< test_arg
allow.extra.arg = TRUE 
#>
# The block above allows the user to add extra arguments to the call to qplot, i.e. qplot(x,y,xlab="The variable x"), would also pass the test.
```


#< quiz "prime"
question: What is the 'oddest' prime?
sc:
    - 2*
    - 3
    - 5
    - 7
success: Well, of course the answer is debatable...
failure: Try again.
#>

Note: A quiz as specified below only works in the shiny environment. If you want to design a quiz in an RMarkdown based RTutor problem set, you should use a chunk. E.g. as follows:

Which of the following numbers is the oddest prime? 2,3,5 or 7? Enter you solution in the code below and press "check".

```{r}
2
```
#< award "The oddest prime"
Wouldn't you agree that the only even prime is the odd man out?
#>

## Exercise Submitting your solution

To submit your solution please proceed as follows:

1. Scroll to the top and click on the icon with the bars <i class="fa fa-tasks fa-fw"></i> to see how many points you got so far. If you want to have more points you can try to solve the missing tasks.

2. If you want to submit click on the download button <i class="fa  fa-download fa-fw"></i> at the very right.

3. In the opened tab click the button "Download Submission File". Your browser should then download a file with the extension `.sub`.

4. Upload that downloaded file to your course management system like Moodle, as specified by your instructor.



